\documentclass[12pt,letterpaper]{article}
\usepackage{fullpage}
\usepackage[top=2cm, bottom=4.5cm, left=2.5cm, right=2.5cm]{geometry}
\usepackage{amsmath,amsthm,amsfonts,amssymb,amscd}
\usepackage{lastpage}
\usepackage{enumerate}
\usepackage{fancyhdr}
\usepackage{mathrsfs}
\usepackage{xcolor}
\usepackage{graphicx}
\usepackage{listings}
\usepackage{hyperref}
\usepackage[nodayofweek, level]{datetime}
\usepackage{bbm}
\usepackage{cases}

\setlength{\parindent}{0.0in}
\setlength{\parskip}{0.05in}


%% ----- COMMANDS -----
% Headings
\newcommand\course{Project Writeup} % Edit for course name
\newcommand{\theorem}[1]{\underline{\textbf{#1}} \\}

% Notation
\newcommand{\set}[1]{\{#1\}}
\newcommand{\C}{\mathbb{C}}
\newcommand{\N}{\mathbb{N}}
\newcommand{\Q}{\mathbb{Q}}
\newcommand{\R}{\mathbb{R}}
\newcommand{\Z}{\mathbb{Z}}
\newcommand{\inv}{^{-1}}
\newcommand{\modulo}[1]{\text{ mod }#1}
\newcommand{\kernel}[1]{\text{ker }#1}
\newcommand{\LeftImplies}{\underline{$\Leftarrow$:} }
\newcommand{\RightImplies}{\underline{$\Rightarrow$:} }
\newcommand{\cycle}[1]{\langle #1 \rangle}
\newcommand{\B}[1]{\mathbf{#1}}

\pagestyle{fancyplain}
\headheight 35pt
\rhead{\course}
\lfoot{}
\cfoot{}
\headsep 1.5em

\fancypagestyle{firststyle}
{
  \fancyhf{}
  \headheight 35pt
  \chead{\textbf{\Large Theory}} % Edit for title
  \rhead{\course \\ Zade Johnston}
  \lfoot{}
  \cfoot{}
  \rfoot{\small\thepage}
  \headsep 1.5em
}

\begin{document}
What to do over next week or so
\begin{itemize}
  \item Continue writing structure function and spectrum code.
  \item Get python code working on Thunderbird.
  \item Replace Athena src folder on both laptop and thunderbird.
  \item Make sure CGL configures right as it is not compiling.
  \item Run MHD simulations using Athena (compile as Jono said in email), comparing equations of state:
  \begin{itemize}
    \item Adiabatic - the usual MHD. Want to compare spectrum/structure function with CGl
    \item CGL - first set $\nu_c\gg 1 \sim 10^8$ and compare with adiabatic. Also want $\beta=2p/B\gg 1$, so set $p=10$ or $100$. Note that this will take longer to run as sound waves travel faster meaning time step has to be shortened.
  \end{itemize}
  \item Decrease $\nu_c$ to try observe interesting effects that Jono wants to look at.
\end{itemize}
Don't be shy to ask Romain, and don't work on too many things at a time just yet.

\textbf{Project Aim:} To look at turbulence in weakly collisonal plasma when $|\Delta p|\sim B^2$ using the Braginskii approximation, and use this to try gain insight into properties of the solar wind.


\end{document}
